---
title: "Time characteristics"
output: 
  html_document: 
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(openair)
```

## Basic information of various pollutants

From the figure below, you can see the time series, frequency distribution and statistical analysis of the six pollutants (average value, median /95% quantile value, minimum /maximum value, missing value data amount / proportion).

```{r echo=TRUE, message=FALSE, warning=FALSE}
summaryPlot(data[,-1])
```

## Daily characteristics

### AQI

```{r echo=TRUE, message=FALSE, warning=FALSE}
calendarPlot(data, 
             pollutant = "AQI",
             breaks=c(-1,0,50,100,200,300,1000),
             labels=c("excellent",
                      "good",
                      "Mild pollution",
                      "moderate pollution",
                      "heavy pollution",
                      "serious pollution"))
```


### PM2.5

```{r echo=TRUE, message=FALSE, warning=FALSE}
calendarPlot(data,pollutant = "PM25")
```

### PM10

```{r echo=TRUE, message=FALSE, warning=FALSE}
calendarPlot(data,pollutant = "PM10")
```

### SO2

```{r echo=TRUE, message=FALSE, warning=FALSE}
calendarPlot(data,pollutant = "SO2")
```

### CO

```{r echo=TRUE, message=FALSE, warning=FALSE}
calendarPlot(data,pollutant = "CO")
```

### NO2

```{r echo=TRUE, message=FALSE, warning=FALSE}
calendarPlot(data,pollutant = "NO2")
```

### O3

```{r echo=TRUE, message=FALSE, warning=FALSE}
calendarPlot(data,pollutant = "O3")
```

## Monthly characteristics

```{r echo=TRUE, message=FALSE, warning=FALSE}
timePlot<-timeVariation(data,pollutant = c("AQI","PM25","PM10","SO2","CO","NO2","O3"),statistic = "mean",xlab = c("month", "weekday"))
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
plot(timePlot,subset = "month")
```

## Weekly characteristics

### AQI

```{r echo=TRUE, message=FALSE, warning=FALSE}
plot(timeVariation(data,pollutant = c("AQI"),statistic = "mean"),subset="day",xlab = c("month", "weekday"))

```

### Other's 

***Just look at the big pictures***

```{r echo=TRUE, message=FALSE, warning=FALSE}
plot(timeVariation(data,pollutant = c("PM25"),statistic = "mean"),subset="day")
plot(timeVariation(data,pollutant = c("PM10"),statistic = "mean"),subset="day")
plot(timeVariation(data,pollutant = c("SO2"),statistic = "mean"),subset="day")
plot(timeVariation(data,pollutant = c("CO"),statistic = "mean"),subset="day")
plot(timeVariation(data,pollutant = c("NO2"),statistic = "mean"),subset="day")
plot(timeVariation(data,pollutant = c("O3"),statistic = "mean"),subset="day")
```
